Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-03 Report/time_correlated.tex
antti changes

We discuss the performance of the \ac{JSFRA} algorithm for different \me{\ell_q} over multiple transmission slots. It is compared to the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users. Fig. \ref{fig-time-analysis} plots the performances of the centralized algorithms for different \me{\ell_q} values. Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and they follow the Poisson process. We considered a \me{4 \times 1} \ac{MIMO} with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}. The \ac{PL} is modeled as a uniform random variable \me{[0,-3]} dB.

Fig. \subref*{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot. The performance of the \ac{JSFRA} scheme using \me{\ell_2} is similar to the \ac{Q-WSRME} approach in the average number of residual packets after each transmission slot. Note that the additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence. Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are larger than those of the actual transmissions. Fig. \ref{fig-time-analysis} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel. Fig. \ref{fig-time-analysis} highlights that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is in the stable region. On contrary, the performance is inferior in the unstable region, since the fair allocation is not effective when the number of backlogged packets is large for all users.

>>>>

In this section, we numerically study the performance of the centralized algorithms with different \me{\ell_q} values over multiple transmission slots. The system model examined for the illustrations is provided in Fig. \ref{fig-time-analysis}. For all users in the system, the average arrivals \me{A_k}'s are fixed and varied equally for the model considered in Fig. \subref*{fig-review}, and for Fig. \subref*{fig-review-time}, the average arrival is fixed to be \me{A_k = 6} bits. Note that the instantaneous arrivals \me{\lambda_k(i)} are all different and it follows the Poisson process. The \ac{PL} is modeled as a uniform random variable \me{[0,-6]} dB.

Fig. \subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \Sigma_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}. Unlike the \ac{Q-WSRM} scheme, the average backlogged packets of the \me{\ell_2} \ac{JSFRA} scheme is comparable to the \ac{Q-WSRME} approach for all average arrival rates due to the explicit rate constraints \eqref{eqn-3.1.4}. However, when \me{A_k \geq 7} bits in Fig. \subref*{fig-review}, both \ac{Q-WSRM} and \ac{Q-WSRME} schemes perform the same since the problem of over-allocation is negligible. The performance of the \me{\ell_1} \ac{JSFRA} scheme outperforms all other schemes in terms of the average number of residual packets due to the greedy allocation at each instant.

Fig. \subref*{fig-review} also includes the uncoordinated \me{\ell_1} \ac{JSFRA} scheme and the \ac{TDM} mode without considering the inter-cell interference terms in the \ac{SINR} expressions while designing the precoders. The \ac{TDM} scheme with the fixed total power constraint performs inferior to the uncoordinated transmission due to the diverse user \ac{PL} variations considered. Fig. \subref*{fig-review-time} compares the total number of backlogged packets left in the system after each transmission slot by different centralized algorithms. The total number of residual packets for the \ac{Q-WSRM} scheme is noticeably large in comparison with the other schemes in Fig. \subref*{fig-review-time} due to the inability in controlling the over-allocations at each instant. The instantaneous fairness constraint imposed by the \me{\ell_\infty} \ac{JSFRA} scheme is effective in reducing the number of backlogged packets for the average arrival rate considered in Fig. \subref*{fig-review-time}. However, in Fig. \subref*{fig-review}, the \me{\ell_\infty} \ac{JSFRA} performs inferior to the \ac{Q-WSRM} scheme, since the fairness is not effective when the system is unstable, \textit{i.e}, when \me{A_k \geq 7} in the current model.
